Quantifying the Impact \\ of Performance Improvements and Cost Reductions \\ from 20 years of Light-Emitting Diode Manufacturing

### 2021-03-18 1_SSL_SPIE/article/main.tex
added missing author names

% Option to view page numbers
\pagestyle{empty} % change to \pagestyle{plain} for page numbers   
\setcounter{page}{301} % Set start page numbering at e.g. 301

@@

\clearpage
% References
\bibliography{main} % bibliography data in main.bib
\bibliographystyle{spiebib} % makes bibtex use spiebib.bst

>>>>

% Option to view page numbers
\pagestyle{plain} % change to \pagestyle{plain} for page numbers   
\setcounter{page}{1} % Set start page numbering at e.g. 301

@@

\clearpage
% References
\bibliography{main} % bibliography data in report.bib
\bibliographystyle{spiebib} % makes bibtex use spiebib.bst
